### 2024-06-18 basic-statistics.qmd
20240618 - tweaks

The mean of $X$ ($\bar{X}$) is calculated as:

@@

The mode is the most common value.

@@

The (sample) variance of $X$ ($s^2$) is calculated as:

@@

The (sample) standard deviation of $X$ ($s$) is calculated as:

@@

: Twelve Misconceptions About *p*-Values from @Goodman2008. Goodman also provides a discussion about why each is false. {#tbl-pValueMisconceptions}

>>>>

The mean of $X$ (written as: $\bar{X}$) is calculated as:

@@

The mode is the most common/frequent value.

@@

The (sample) variance of $X$ (written as: $s^2$) is calculated as:

@@

The (sample) standard deviation of $X$ (written as: $s$) is calculated as:

@@

: Twelve Misconceptions About *p*-Values from @Goodman2008. Goodman also provides a discussion about why each statement is false. {#tbl-pValueMisconceptions}
